Neutron Star Mergers and their Impact on Second Generation Star Formation in the Early Universe

### 2023-09-14 NSM_Skinner_Wise/NSM_mixing.tex
Bringing abstract to word limit. Resubmitting.

% Abstract of the paper
\begin{abstract}
	The exact evolution of elements in the universe, from primordial hydrogen and helium to heavier elements like gold and platinum produced via the r-process, is still under scrutiny. The supernova deaths of the very first stars to form in the universe led to the enrichment of their local environments with new metals, and can leave behind neutron stars as remnants. These remnants can end up in binary systems with other neutron stars, and eventually merge, allowing for the r-process to occur. In this work, we study the scenario where a single neutron star merger (NSM) enriches a halo early in its evolution to understand the impact on the second generation of stars and their metal abundances. We perform a suite of high resolution cosmological zoom-in simulations using \enzo{} where we have implemented a new NSM model varying the explosion energy and the delay time. In general, a NSM leads to a significant r-process enhancement in the second generation of stars \textbf{in a galaxy with a stellar mass of $\sim 10^5 \Ms$ at redshift 10.  A high explosion energy leads to a Pop II mass fraction of 72\% being highly enhanced with r-process elements, while a lower explosion energy leads to a Pop II mass fraction of 80\% being r-process enhanced, but only 14\% being highly enhanced. When the NSM has a short delay time of 10 Myr, only 5\% of the mass fraction of Pop II stars is highly r-process enhanced, while 64\% of the mass fraction of Pop II stars is highly r-process enhanced for the longest delay time of 100 Myr.} This work represents a stepping stone towards understanding how NSMs impact their environments and metal abundances of descendant generations of stars.
\end{abstract}

>>>>

% Abstract of the paper
\begin{abstract}
	The exact evolution of elements in the universe, from primordial to heavier elements produced via the r-process, is still under scrutiny. The supernova deaths of the very first stars led to the enrichment of their local environments, and can leave behind neutron stars (NS) as remnants. These remnants can end up in binary systems with other NSs, and eventually merge, allowing for the r-process to occur. We study the scenario where a single NS merger (NSM) enriches a halo early in its evolution to understand the impact on the second generation of stars and their metal abundances. We perform a suite of high resolution cosmological zoom-in simulations using \enzo{} where we have implemented a new NSM model varying the explosion energy and the delay time. In general, a NSM leads to significant r-process enhancement in the second generation of stars \textbf{in a galaxy with a stellar mass of $\sim 10^5 \Ms$ at redshift 10.  A high explosion energy leads to a Pop II mass fraction of 72\% being highly enhanced with r-process elements, while a lower explosion energy leads to 80\% being enhanced, but only 14\% being highly enhanced. When the NSM has a short delay time of 10 Myr, only 5\% of the mass fraction of Pop II stars is highly enhanced, while 64\% is highly enhanced for the longest delay time of 100 Myr.} This work represents a stepping stone towards understanding how NSMs impact their environments and metal abundances of descendant generations of stars.
\end{abstract}
